\label{Section: Simulation}
\section{Simulation}
\subsection{Simulation Platform}
\begin{frame}{Simulation Platform}
    \label{Simulation: Control Structure of Chemical Reactor}
    The simulation object is a chemical reactor whose control structure is shown as the following figure.\\[-10pt]
    \begin{center}
      \input{Figures/Simulation/Control.Structure.of.Chemical.Reactor.tex}
    \end{center}
\end{frame}

\begin{frame}{Simulation Platform}
    \label{Simulation: Structure of Simulation Platform}
    The simulation platform is implemented in Matlab, which consists of three modules: an evidence generator, an incident prediction module, and a risk assessment module.
    \begin{center}
      \input{Figures/Simulation/Structure.of.Simulation.Platform.tex}
    \end{center}
\end{frame}

\begin{frame}{Simulation Platform}
    \label{Simulation: Multi-Level Bayesian Network of Reactor}
    The multi-level Bayesian network of the chemical reactor is shown as following figure.\vspace{-18pt}\\
    \begin{center}
      \input{Figures/Simulation/Multi-Level.Bayesian.Network.of.Reactor.tex}
    \end{center}
\end{frame}

\begin{frame}{Simulation Platform}
    \label{Simulation: Evidences List}
    The list of evidences is shown as following table.

    \taburowcolors[2] 2{black!10 .. black!30}
    \extrarowsep = 1mm
    \begin{tabu} to \textwidth{*2{X[c,-1]|[1.5pt white]}X[l]|[1.5pt white]X[-1, c]}
    \rowcolor{black!80}\rowfont\bfseries \textcolor{white}{Start}  & \textcolor{white}{End} & \textcolor{white}{Description} & \textcolor{white}{Symbol}\\\tabucline[1.5pt white]{-}
    50            & 60        & IP sweep                         & $L(a_1)$ \\\tabucline[1.5pt white]{-}
    75            & 110       & Vulnerability scanning           & $L(a_2)$ \\\tabucline[1.5pt white]{-}
    120           & 180       & DoS attack to HDS                & $L(a_6)$ \\\tabucline[1.5pt white]{-}
    157           & 171       & IP address spoofing              & $L(a_9)$ \\\tabucline[1.5pt white]{-}
    259           & 261       & Reconfigure PLC5                 & $L(a_{20})$ \\\tabucline[1.5pt white]{-}
    266           & 378       & Switch function of V4 failed     & $F(f_4)$ \\\tabucline[1.5pt white]{-}
    286           & 390       & Pressure reduce function failed  & $F(f_{12})$ \\\tabucline[1.5pt white]{-}
    310           & 400       & Pressure is excessive            & $H(e_4)$ \\

    \end{tabu}
\end{frame}

\begin{frame}{Simulation Platform}
    \label{Simulation: Quantification of Consequences}
    The quantification of consequences is shown as following table.

    \newcolumntype Z{X[m, c, 1.8]{%
    S[
    %group-four-digits=true ,
    round-mode = figures,
    group-separator = {,},
    add-decimal-zero = false,
    round-integer-to-decimal=true ,
    table-number-alignment = center,
    table-space-text-pre = \hspace{30pt},
    per-mode=symbol]}}
    \tabucolumn Z
    \taburowcolors[2] 2{black!10 .. black!30}
    \tabulinesep = 1mm
    \extrarowsep = 1mm
    \begin{tabu}to \textwidth{X[c,1, m]|[1.5pt white]X[m, 3]|[1.5pt white]Z}

    \rowcolor{black!80}\rowfont\bfseries
        \textcolor{white}{Incident Symbol} &
        \textcolor{white}{Description of Incident} &
        \textcolor{white}{\bf Quantification of Consequence(\$)}\\
    \tabucline[1.5pt white]{-}
        $x_{1}$  & Product damaged              & 50000  \\\tabucline[1.5pt white]{-}
        $x_{2}$  & Tank damaged                 & 500000 \\\tabucline[1.5pt white]{-}
        $x_{3}$  & Heater damaged               & 10000  \\\tabucline[1.5pt white]{-}
        $x_{4}$  & Sensors damaged              & 10000  \\\tabucline[1.5pt white]{-}
        $x_{5}$  & Staff$_{\text{1-4}}$ injured & 800000 \\\tabucline[1.5pt white]{-}
        $x_{6}$  & Staff$_{\text{5-9}}$ injured & 1000000\\\tabucline[1.5pt white]{-}
        $x_{7}$  & Water pollution              & 200000 \\\tabucline[1.5pt white]{-}
        $x_{8}$  & Air pollution                & 200000 \\
    \end{tabu}
\end{frame}

\subsection{Simulation and Result Analysis}
\begin{frame}{Simulation and Result Analysis}
    \label{Simulation: Curvers of Cybersecurity Risk and Incident Probability}
    \begin{center}
      \input{Figures/Simulation/Curver.of.Cybersecurity.Risk.tex}\\
      \input{Figures/Simulation/Curvers.of.Incident.Probability.tex}\\
    \end{center}
\end{frame}

\begin{frame}{Simulation and Result Analysis}
    \label<trans:1>{Simulation: Ability to Deal with the Unknown Attacks Step 1}
    \label<trans:2>{Simulation: Ability to Deal with the Unknown Attacks Step 2}
    \label<trans:3>{Simulation: Ability to Deal with the Unknown Attacks Step 3}
    \vspace{10pt}
    \begin{overlayarea}{\textwidth}{1cm}
        \only<1| trans:1>{In the previous simulation, the curve of the cybersecurity risk is shown as the \textcolor{red}{\bf red} line in the following figure.}
        \only<2| trans:2>{To validate the ability to deal with the unknown attacks, the attack knowledge about attack \textcolor{red}{\st{$a_6$}} and attack \textcolor{red}{\st{$a_9$}} is removed from the multi-level Bayesian network.}
        \only<3| trans:3>{Then an identical multi-step attack on the system is launched to the system. The new cybersecurity risk curve is shown the dashed line in the following figure.}
    \end{overlayarea}\vspace{10pt}
    \begin{center}
      \input{Figures/Simulation/Curvers.of.Cybersecurity.Risk.tex}
    \end{center}
\end{frame}

\begin{frame}{Simulation and Result Analysis}
    \label<trans:1>{Simulation: Curve of Execution Time Distribution Step 1}
    \label<trans:2>{Simulation: Curve of Execution Time Distribution Step 2}
    \label{Simulation: Curve of Execution Time Distribution}
    \vspace{10pt}
    \begin{overlayarea}{\textwidth}{1.8cm}
        \only<1| trans:1>{We repeat the first simulation 5,000 times, and the execution time of 5,000 calculations is recorded. This simulation is run on a machine with Intel Pentium processor G3220 (3M Cache, 3.00GHz) and 4GB DDR3 memory. The following figure shows the distribution of the 5,000 execution times.}
        \only<2-| trans:2>{Some parameters of the following figure:
        \begin{itemize}
           \item<2-> The average execution time of a risk assessment is $94.1$ms.
           \item<3-> The minimum execution time of a risk assessment is $89.9$ms.
           \item<4-> The maximum execution time of a risk assessment is $131.6$ms.
         \end{itemize}}
    \end{overlayarea}\vspace{10pt}
    \begin{center}
      \input{Figures/Simulation/Curve.of.Execution.Time.Distribution.tex}
    \end{center}
\end{frame}

\begin{frame}{Simulation and Result Analysis}
    \label<trans:1>{Simulation: Curves of Risk Assessment Algorithm Scalability Step 1}
    \label<trans:2>{Simulation: Curves of Risk Assessment Algorithm Scalability Step 2}
    \label<trans:3>{Simulation: Curves of Risk Assessment Algorithm Scalability Step 3}
    \vspace{10pt}
    \begin{overlayarea}{\textwidth}{1.8cm}
    \only<1| trans:1>{Finally, 25 multi-level Bayesian networks with different node sizes are adopted to show the possible upper/lower bounds and the scalability of our approach.}
    \only<2| trans:2>{In the following figure, the fitting line $$y = 0.0019x - 0.0175$$ matches well with the correlation coefficient $r = 0.9987$.}
    \only<3| trans:3>{This means that the execution time of the risk assessment scales linearly with the increase of the node size of the multi-level Bayesian network.}
    \end{overlayarea}\vspace{10pt}
    \begin{center}
      \input{Figures/Simulation/Curves.of.Risk.Assessment.Algorithm.Scalability}
    \end{center}
\end{frame}

